WORCS: A Workflow for Open Reproducible Code in Science

### 2020-11-08 paper/reviews_ds.Rmd
number comments

\RC{The claim that WORCS is amenable to the FAIR Guiding Principles should be justified. What are the solutions provided by WORCS that make a project interoperable and reusable? It would be improved with a more thorough discussion on how WORCS meets each FAIR principle.}

@@

\RC{Is WORCS providing any service for de-identification?}

>>>>

\RC{C2: The claim that WORCS is amenable to the FAIR Guiding Principles should be justified. What are the solutions provided by WORCS that make a project interoperable and reusable? It would be improved with a more thorough discussion on how WORCS meets each FAIR principle.}

@@

\RC{C3: Is WORCS providing any service for de-identification?}
